### 2023-10-06 vesicle_code/docs/confinedMulti/response.tex

\noindent
{\bf Response:} This was our oversight. The parameter values for $a$ and
$\epsilon$ were unintentionally reversed. This has been fixed.

%%%%%%%%
\item What motivated the choice of a sigmoid function, Eq.~(9), rather
  than a simple min/max operation so that the bending rigidity does not
    extend past the $[0.1, 1]$ range? Would the use of a regular-mixture
    model, which might be more physically realistic, remove the need for
    such a mathematical approximation as the equilibrium concentrations
    will no longer be $0$ and $1$?

\noindent
{\bf Response:} Because we are using an integral equation formulation,
    we are able to achieve high-order accuracy as long as everything is
    smooth, including the vesicle shape, tension, and the bending
    stiffness. If we used any kind of $\max$ or $\min$ function, the
    bending modulus would lose differentiability and this would result
    in a loss of accuracy. We have expanded the text to explain this
    point.

    We are unsure what the reviewer means by a ``regular-mixture model".
    If they mean a linear parameterization between the stiff and floppy
    phases, this is exactly equation (8).  We originally used this
    choice, but as argued in the manuscript, because of the strong
    confinement, the lipid concentration could easily exceed a value of
    $1$, and this resulted in a unphysical negative bending modulus
    which ultimately leads to an instability.  Figure 2 demonstrates
    this effect. Furthermore, Figure 3 validates the choice of the
    sigmoid parameterization by comparing the results with a result from
    the literature that used the linear parameterization in an unbounded
    linear shear flow.

@@

%%%%%%%%
\item Please define $\eta$ in Eq.~(10).

\noindent
{\bf Response:} $\eta$ is the stress density that is used to satisfy the
    Dirichlet boundary condition on the solid walls. The text has been
    adjusted.

@@

%%%%%%%%
\item Please define $\mathbf{U}$ in Eq.~(15). Is this the velocity of
  the interface?

{\bf Response:} This is the prescribed velocity along the solid wall
    which is a combination of no-slip along the top and bottom of the
    channel, and a Poiseuille flow at the inlet and outlet. We now
    reference equation (3), which defines $\mathbf{U}$, immediately
    after equation (15).

%%%%%%%%
\item What value of $\delta$ is used to determine the lubrication layer
  thickness?

{\bf Response:} We used $\delta = 0.3$. For the stenosis geometry, this
corresponds to a lubrication layer thickness of size a little less than
one micron.

@@

%%%%%%%%
\item The simulation parameters must be provided. In the stenosis case
  what is the (dimensionless) width of the constricted region? For the
    contracting geometry case what does a $2~\mu$m wide neck correspond
    to?

{\bf Response:} We have included dimensionless values for the stenosis
geometry, contracting geometry, and vesicle length. To convert to
dimensioned units, the length scale 3.17 microns can be used.

@@

%%%%%%%%
\item The authors measure the tangential velocity at 4 points. They
  should provide some justification for this number. Also, it is
    advisable that in Figure 7, the authors use a different color for
    each velocity plot. The plot looks highly convoluted and does not
    convey the message clearly. Also, what are the bounds within which
    the authors call the tangential velocity to be constant in Figure 7?
    They should define a bound for the variation that could be
    considered constant. Moreover, in Figure 7, for the floppy vesicle,
    the authors see a large deviation for the tangential velocity. It
    doesn't seem like the velocity could be called `constant'. The
    authors should provide a more detailed explanation for this.

\noindent
{\bf Response:} A response

%%%%%%%%
\item In some simulations, the authors choose a `random' initial
  condition. It would be helpful if they could mathematically define the
    function for this initial condition.

\noindent {\bf Response:} The examples with a random initial condition
    use the uniform distribution with the range $[0,1]$ to define the
    lipid concentration $u$ at each spatial point. Given the choices of
    $b_{\min}=0.1$ and $b_{\max}=1$, the resulting mean bending
    stiffness is $\overline{b(u)} \approx 0.55$. The text has been
    adjusted at the start of Section 3.1 and Section 3.2.

@@

%%%%%%%%
\item In Figure 6, the author should comment on the energy behavior of
  the floppy vesicle in the stenosis region.

\noindent
{\bf Response:} We have included a discussion of the energy behavior of
the floppy vesicle and compared it with the stiff case.

### 2023-10-06 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on revisions

To avoid tangling, the vesicle membrane is parameterized in terms of the
$\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed
vesicle length and $\theta$ is the angle between the tangent vector and
the positive $x$-axis. This requires decomposing the velocity field on
$\gamma$ into a normal velocity $V$ and tangential velocity $T$. Then,
the no-slip boundary condition for the vesicle velocity is
\begin{align}
  \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is satisfied by requiring that
$\eeta$ satisfies
\begin{align}
  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma,
  \label{eqn:DLP_BIE}
\end{align}
\textcolor{blue}{
where the fluid velocity $\UU$ on the solid wall $\Gamma$ is defined in
Equation~\eqref{eqn:dirBC}.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LL} Lubrication layers and excess pressure}
The lubrication layer between a vesicle and the solid wall plays a
critical role in the dynamics of a vesicle under strong confinement.
Therefore, throughout Section~\ref{sec:results}, we calculate and
analyze the flow inside the lubrication layers between the vesicle and
the channel walls to elucidate the correlation between hydrodynamics and
membrane dynamics. To define the size of the top lubrication layer, we
let $d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point
on the vesicle, $\xx \in \gamma$, and the top half of the confining
geometry. The size of the bottom lubrication layer is defined similarly.
We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with the
condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, where $\delta$ is
a parameter. If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
width is
\begin{align}
  w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
    \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The region that defines the top and bottom lubrication layers is
illustrated in Figure~\ref{fig:schematic}, and the height of the gray
regions, 
\textcolor{blue}{
$w_{\mathrm{top}}$ and $w_{\mathrm{bot}},$
}
denote the lubrication layer thicknesses. In this example, the top layer
is broken across two different regions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). All the multicomponent examples have floppy-to-stiff
ratio $\beta = 10^{-1}$. For the single-component case, we consider two
bending stiffnesses: $b(u) = 1$ and $b(u) = 0.55$. We refer to these
cases as a stiff single-component vesicle and a floppy single-component
vesicle, respectively. The smaller bending stiffness represents the
average bending stiffness of a multicomponent vesicle, when its stiff
and floppy regions cover the same amount of area. Throughout this
section we plot the position of the vesicle in terms of the
$x$-coordinate of its center of mass. For the stenosis geometry in
Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and
ends at $x=15$. For the contracting geometry in
Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
and reaches its narrowest point at $x=15$.

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$. With the
current setup and $Ca=0.25$, an elliptical vesicle with reduced area
greater than $\alpha = 0.8$ cannot fit through the closely-fitting
geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. 
\textcolor{blue}{
The lipid distribution at each point on the multicomponent vesicle is
chosen randomly from the uniform distribution with the range $[0,1]$.
Since $b_{\min}=0.1$ and $b_{\max}=1$, the mean bending stiffness is
$\overline{b(u)} \approx 0.55$.}
%The lipid distribution of the multicomponent vesicle is
%initially random with a mean value of 0.55. 
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new sigmoid bending modulus in Equation~\eqref{eqn:tanhBending}. A
single Lagrangian point is included to visualize any tank-treading
behavior. There are slight differences between the three cases, with the
most noticeable being that the multicomponent vesicle has higher
curvature in the floppy region. However, in general, there is little
difference between these cases, principally because these vesicles have
a large reduced area.

@@

We next consider a vesicle with a smaller reduced area $\alpha=0.4$ with
the same geometry and capillary number. Figure~\ref{fig:RA4} shows the
shape of a (a) stiff single-component, (b) floppy single-component, and
(c) multicomponent vesicle at six locations along the stenosis channel.
Contrary to the vesicles with the larger reduced area
(Figure~\ref{fig:RA6}), the bending modulus has a large effect on the
vesicle shape. We first consider the three different energies---bending,
tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
plot these energies as a function of the vesicle's center. Note that the
single-component vesicles do not have a phase energy. We observe that,
as the vesicle enters the stenosis, it develops regions of high
curvature, and this results in an increase in the bending energy. As
the stiff single-component and multicomponent vesicles reach a
steady-state shape near the middle of the channel, their bending and
tension energies remain nearly constant from $x=0$ until the end of the
stenosis. 
\textcolor{blue}{
For the floppy case, the bending energy is similar in size as the stiff
case. Since the floppy bending modulus is ten-times smaller than the
stiff case, this indicates that the curvature of the floppy vesicle is
about $\sqrt{10}$-times larger than the stiff case. This additional
curvature corresponds to larger and more dynamic membrane deformations,
and a more varying tension energy.}
For the multicomponent vesicle, the phase energy is also nearly constant
in this region. This implies that there is no coarsening of lipid phase
parameter in the middle of a stenosis.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a vesicle passing through a channel that
slowly contracts to a  2~$\mu$m wide neck, and then
immediately opens up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
area $\alpha = 0.5$ with different initial lipid distributions are
illustrated. The initial distributions are (a) random, (b) stiff in the
front and floppy in the back, and (c) floppy in the front and stiff in
the back. 
\textcolor{blue}{
As previously mentioned, the initial random lipid distributions are
sampled from the uniform distribution with the range $[0,1]$.}
The vesicle with the random initial lipid distribution quickly
phase separates into two floppy and two stiff regions. As seen in the
stenosis geometry, further phase separation is delayed until the vesicle
is no longer under strong confinement. The vesicle with the stiff region
at the front maintains its orientation. In contrast, the vesicle with
the floppy region on the front reorients the floppy region towards the
back of the vesicle. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in subsequent
simulations, we initialize the vesicle's lipid concentration so that the
floppy region is in the back and its stiff region is in the front. The
vesicle shapes develop regions with high curvature in the floppy region
when they first pass through the narrowest part of the geometry, but
once the strong confinement is abruptly removed, these regions of high
curvature are quickly smoothed.

>>>>

To avoid tangling, the vesicle membrane is parameterized in terms of the
$\theta$-$L$ variables~\cite{hou-low-she1994}, where $L$ is the fixed
vesicle length and $\theta$ is the angle between the tangent vector and
the positive $x$-axis. This requires decomposing the velocity field on
$\gamma$ into a normal velocity $V$ and tangential velocity $T$. Then,
the no-slip boundary condition for the vesicle velocity is
\begin{align}
  \frac{d\xx}{dt} = V \nn + T \ss + D[\eeta](\xx), \quad \xx \in \gamma.
\end{align}
The boundary condition on $\Gamma$ is satisfied by requiring that
$\eeta$ satisfies
\begin{align}
  \UU(\xx) = -\frac{1}{2}\eeta(\xx) + 
    S[\ff](\xx) + D[\eeta](\xx), \quad \xx \in \Gamma,
  \label{eqn:DLP_BIE}
\end{align}
\textcolor{blue}{
where the fluid velocity $\UU$ on the solid wall $\Gamma$ is defined
in~\eqref{eqn:dirBC}.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{sec:LL} Lubrication layers and excess pressure}
The lubrication layer between a vesicle and the solid wall plays a
critical role in the dynamics of a vesicle under strong confinement.
Therefore, throughout Section~\ref{sec:results}, we calculate and
analyze the flow inside the lubrication layers between the vesicle and
the channel walls to elucidate the correlation between hydrodynamics and
membrane dynamics. To define the size of the top lubrication layer, we
let $d(\xx,\Gamma_\mathrm{top})$ be the minimum distance between a point
on the vesicle, $\xx \in \gamma$, and the top half of the confining
geometry. The size of the bottom lubrication layer is defined similarly.
We find all local minimums of $d(\xx,\Gamma_\mathrm{top})$, with the
condition that $d(\xx,\Gamma_\mathrm{top}) < \delta$, 
\textcolor{blue}{
where we use the parameter value $\delta = 0.3$.
}
%where $\delta$ is a parameter.
If no such local minimums exist, then the vesicle is too
far from $\Gamma_\mathrm{top}$ to define a lubrication layer. If there
are two or more local minimums, the left-most, $\xx_L$, and right-most,
$\xx_R$, local minimums form the start and end of the lubrication layer.
If there is only one local minimum, then $\xx_L$ and $\xx_R$ are the
points on $\gamma$ to the left and right of this local minimum with the
condition that $d(\xx_L,\Gamma_\mathrm{top}) =
d(\xx_R,\Gamma_\mathrm{top}) = \delta$. Then, the segment
$\gamma_{\mathrm{layer}} \subset \gamma$ consists of all points $\xx \in
\gamma$ between $\xx_L$ and $\xx_R$ with the condition that
$d(\xx,\Gamma_\mathrm{top}) < \delta$. Finally, the lubrication layer
width is
\begin{align}
  w_\mathrm{top} = \frac{1}{|\gamma_{_\mathrm{layer}}|} 
    \int_{\gamma_{_\mathrm{layer}}} d(\xx,\Gamma_\mathrm{top}) \, ds.
\end{align}
The region that defines the top and bottom lubrication layers is
illustrated in Figure~\ref{fig:schematic}, and the height of the gray
regions, 
\textcolor{blue}{
$w_{\mathrm{top}}$ and $w_{\mathrm{bot}},$
}
denote the lubrication layer thicknesses. In this example, the top layer
is broken across two different regions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:results}Hydrodynamics of a multicomponent vesicle
under strong confinement}
We consider both a single-component and a multicomponent vesicle
\textcolor{blue}{
with a fixed dimensionless length of $L = 7.4$
}
suspended in two geometries: a closely-fitting geometry (stenosis) and a
geometry that slowly contracts to a narrow neck and then quickly widens
(contracting). All the multicomponent examples have floppy-to-stiff
ratio $\beta = 10^{-1}$. For the single-component case, we consider two
bending stiffnesses: $b(u) = 1$ and $b(u) = 0.55$. We refer to these
cases as a stiff single-component vesicle and a floppy single-component
vesicle, respectively. The smaller bending stiffness represents the
average bending stiffness of a multicomponent vesicle, when its stiff
and floppy regions cover the same amount of area. Throughout this
section we plot the position of the vesicle in terms of the
$x$-coordinate of its center of mass. For the stenosis geometry in
Section~\ref{subsec:Stenosis}, the narrow region begins at $x=-15$ and
ends at $x=15$. For the contracting geometry in
Section~\ref{subsec:Contraction}, the geometry begins to narrow at $x=4$
and reaches its narrowest point at $x=15$.

@@

We start by considering a vesicle with reduced area $\alpha = 0.6$
passing through stenosis with a capillary number $Ca = 0.25$. 
\textcolor{blue}{
The dimensionless width of the stenosis starts at $6.8$ and narrows to
$1.4$. 
}
With the current setup and $Ca=0.25$, an elliptical vesicle with reduced
area greater than $\alpha = 0.8$ cannot fit through the closely-fitting
geometry. Figure~\ref{fig:RA6} shows six time steps of a (a) stiff
single-component (b) floppy single-component, and (c) multicomponent
vesicle. 
\textcolor{blue}{
The lipid distribution at each point on the multicomponent vesicle is
chosen randomly from the uniform distribution with the range $[0,1]$.
Since $b_{\min}=0.1$ and $b_{\max}=1$, the mean bending stiffness is
$\overline{b(u)} \approx 0.55$.}
%The lipid distribution of the multicomponent vesicle is
%initially random with a mean value of 0.55. 
In all plots, the color is the dimensionless bending modulus of the
multicomponent vesicle that remains bounded in $[0.1,1]$ by using the
new sigmoid bending modulus in Equation~\eqref{eqn:tanhBending}. A
single Lagrangian point is included to visualize any tank-treading
behavior. There are slight differences between the three cases, with the
most noticeable being that the multicomponent vesicle has higher
curvature in the floppy region. However, in general, there is little
difference between these cases, principally because these vesicles have
a large reduced area.

@@

We next consider a vesicle with a smaller reduced area $\alpha=0.4$ with
the same geometry and capillary number. Figure~\ref{fig:RA4} shows the
shape of a (a) stiff single-component, (b) floppy single-component, and
(c) multicomponent vesicle at six locations along the stenosis channel.
Contrary to the vesicles with the larger reduced area
(Figure~\ref{fig:RA6}), the bending modulus has a large effect on the
vesicle shape. We first consider the three different energies---bending,
tension, and phase---for each example. In Figure~\ref{fig:Energy}, we
plot these energies as a function of the vesicle's center. Note that the
single-component vesicles do not have a phase energy. We observe that,
as the vesicle enters the stenosis, it develops regions of high
curvature, and this results in an increase in the bending energy. As
the stiff single-component and multicomponent vesicles reach a
steady-state shape near the middle of the channel, their bending and
tension energies remain nearly constant from $x=0$ until the end of the
stenosis. 
\textcolor{blue}{
For the floppy case, the bending energy is similar in size as the stiff
case. Since the floppy bending modulus is about two-times smaller than the
stiff case, this indicates that the curvature of the floppy vesicle is
about $\sqrt{2}$-times larger than the stiff case. This additional
curvature corresponds to larger and more dynamic membrane deformations,
and a more varying tension energy.}
For the multicomponent vesicle, the phase energy is also nearly constant
in this region. This implies that there is no coarsening of lipid phase
parameter in the middle of a stenosis.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a vesicle passing through a channel that
slowly contracts 
\textcolor{blue}{
from a dimensionless width of $6.5$ to $0.63$,
}
and then immediately opens back up to a channel 
\textcolor{blue}{
with width $6.5$. In dimensioned units, the width of the neck is
$2~\mu$m.
}
We first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
area $\alpha = 0.5$ with different initial lipid distributions are
illustrated. The initial distributions are (a) random, (b) stiff in the
front and floppy in the back, and (c) floppy in the front and stiff in
the back. 
\textcolor{blue}{
As previously mentioned, the initial random lipid distributions are
sampled from the uniform distribution with the range $[0,1]$.}
The vesicle with the random initial lipid distribution quickly
phase separates into two floppy and two stiff regions. As seen in the
stenosis geometry, further phase separation is delayed until the vesicle
is no longer under strong confinement. The vesicle with the stiff region
at the front maintains its orientation. In contrast, the vesicle with
the floppy region on the front reorients the floppy region towards the
back of the vesicle. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in subsequent
simulations, we initialize the vesicle's lipid concentration so that the
floppy region is in the back and its stiff region is in the front. The
vesicle shapes develop regions with high curvature in the floppy region
when they first pass through the narrowest part of the geometry, but
once the strong confinement is abruptly removed, these regions of high
curvature are quickly smoothed.
